Modeling defoliation of Pinus Radiata trees using hyperspectral remote sensing data

### 2018-08-03 01_writing/Schratz_hyperspectral.tex
add discussion about 7 vars model

Using only the seven most important variables (\autoref{fig:var-imp}) shows small increases in performance for Laukiz 1 and Laukiz 2, a small decrease for Luiando and almost a reduction of 50\% of the error for Oiartzun (32.97 vs. 17.62 RMSE).

@@

@@

An important point that needs to be considered when interpreting the performance results is that we only related defoliation to indices derived from remote sensing data.
Possible other cofounding factors that could possibly help in predicting defoliation were not considered.
One example here is tree age: The older a tree the more vunerable it may be to pathogen infections causing defoliation.
However, such predictors would not be available for a spatial prediction scenario and one of the main goals of this study is to relate defoliation to variables that are available on a larger scale (e.g. remote sensing indices).

	[COMPARE ALL VARIABLES VS 7 VARIABLES]

@@

@@

It is not surprising that vegetation indices are most important for the model as they are most sensitive to changes in vegetation health.
Even though we are not specifically looking at vegetation health but at the level of defoliation, these indices seem to help the model deciding whether a tree is defoliated or not.
The vegetation indeces could help here in two ways:
1) Trees that show a high level of defoliation do also reflect their bad health status through the remaining foliation.
2) Defoliated trees have more influence of bare ground information in their pixel values and will therefore be identified as defoliated by the model.

Even though no NRI made it among the most important variables in this study (stating that the first seven of this study are the most important ones), it is interesting that they occupy all ranks from 8 - 30 (\autoref{fig:var-imp}).
Our statement saying that the important indices of this study are the first seven can be seen critical as we only based the selection on a visual inspection of the variable importance results (\autoref{fig:var-imp}).
All indices starting from rank eight do simply have a very small score.
Nevertheless, one could also make the cut at rank five here.
However, the break between vegetation indeces and NRI at rank eight also had an influence in setting this subjective break there.

>>>>

Using only the seven most important variables (\autoref{fig:var-imp}) for the super model shows small increases in performance for Laukiz 1 and Laukiz 2, a small decrease for Luiando and almost a reduction of 50\% of the error for Oiartzun (32.97 vs. 17.62 RMSE) (\autoref{tab:supermodel_performance}).

@@

\subsection{Spatial prediction}

@@

An important point that needs to be considered when interpreting the performance results is that we only related defoliation to indices derived from remote sensing data.
Possible other cofounding factors that could possibly help in predicting defoliation were not considered.
One example here is tree age: The older a tree the more vulnerable it may be to pathogen infections causing defoliation.
However, such predictors would not be available for a spatial prediction scenario and one of the main goals of this study is to relate defoliation to variables that are available on a larger scale (e.g. remote sensing indices).

@@

An interesting find is that the supermodel with only seven variables shows a better overall performance than the model with all 7471 variables (\autoref{tab:supermodel_performance}).
This leads to the conclusion that adding as many variables as possible to a model will not necessarily improve its performance.
In contrast, too much information can even be problematic for the model as it will have a hard time prioritizing variables.
However, to find the most important variables in the first place and to check for the performance difference, a model with all variables needs to fitted first.
This scenario cannot be generalized and different results may occur for other datasets.
Using a model with only a few predictors does not only simplify prediction tasks but also reduces runtime for hyperparameter tuning and performance estimation.

@@

It is not surprising that vegetation indices are most important for the model as they are most sensitive to changes in vegetation health.
Even though we are not directly looking at vegetation health but using the level of defoliation as a proxy, these indices seem to help the model most deciding whether a tree is defoliated or not.
Vegetation indices can help here in two ways:
1) Trees that show a high level of defoliation do also reflect their bad health status through the remaining foliation.
2) Defoliated trees have more influence of bare ground information in their pixel values and will therefore be classified as defoliated by the model.

Even though no NRI made it among the most important variables in this study (stating that the first seven of this study are the most important ones), it is interesting that all ranks from 8 - 30 are occupied by NRI (\autoref{fig:var-imp}).

Our statement saying that the important indices of this study are the first seven can be seen critical as we only based the selection on a visual inspection of the variable importance results (\autoref{fig:var-imp}).
The decision to make a cut between rank seven and eight was based on a combination of two facts: 1) Using only vegetation indices is easier for large scale predictions using satellites like Sentinel-2 (most NRI cannot be used with it) and 2) the drop in the importance score of the variable importance results (\autoref{fig:var-imp}).
However, based on this statement, we could also have made the cut between rank five and 6 but including the two vegetation indices at rank six and seven will eventually improve the model and does not increase runtime.

\section{Conclusion}
